### 2014-03-19 thesis-proposal/parsing.tex
proposal updates

\subsection{Example: Web Search}
We begin in Fig. \ref{f-example} with an example showing several different TSLs being used to define a fragment of a web application showing search results from a database. Note that for clarity of presentation, we color each character  according to the TSL it is governed by.% Black represents the base language.

>>>>

\subsection{Example: Web Search}
We begin in Fig. \ref{f-example} with an example showing several different TSLs being used to define a fragment of a web application showing search results from a database. Note that for clarity of presentation, we color each character  according to the TSL it is governed by. Black represents the base language and comments are in italics.

### 2014-03-19 thesis-proposal/problem.tex
proposal updates

\begin{enumerate}
\item \textbf{Syntax for pattern literals}. An ideal syntax would permit us to express patterns concisely and clearly. For example, The BisI restriction enzyme cuts DNA whenever it sees the pattern \texttt{GC\textit{N}GC}, where \texttt{\textit{N}} represents any base. We would want to express it, perhaps, as follows (using curly braces to splice one pattern into another):
\begin{lstlisting}[numbers=none]
let N : Pattern = <SURLA|T|G|CEURL>
let BisI : Pattern = <SURLGC{EURLNSURL}GCEURL>\end{lstlisting}
%The cognitive load of reading and writing patterns is low and patterns are parsed once at compile-time. 
Malformed patterns would result in intelligible {compile-time} errors.
\item A \textbf{type system} that ensures that key invariants related to regular expressions are statically maintained:
	\begin{enumerate}
	\item only other patterns and properly escaped strings are spliced into a pattern, to avoid splicing errors and injection attacks \cite{owasp2013, Bravenboer:2007:PIA:1289971.1289975}
	\item out-of-bounds backreferences to a captured group are not used \cite{spishak2012type}
	\item string processing operations do not lead to a string that is malformed, when well-formedness can be captured as membership in a regular language \cite{fulton-thesis}
	\end{enumerate}
%When an error is found, an intelligible error message is provided.
%\item An \textbf{implementation} that partially or fully compiles known regular expressions into the efficient internal representation that will be used by the regular expression matching engine (e.g., a finite automata \cite{Thompson:1968:PTR:363347.363387}) ahead of time. In most languages, this compilation step occurs at run-time, even if the pattern is fully known at compile-time, thereby introducing performance overhead into programs. If the developer is not careful to cache compiled representations, regular expressions used repeatedly in a program might be needlessly re-compiled on each use. %By performing this step ahead-of-time, these dangers can be avoided.
\item \textbf{Editor services} to support syntax highlighting of patterns and to allow clients to refer to documentation and interactively test patterns against examples strings (e.g. \cite{IntelliJRegexp}) or even extract patterns from examples interactively (e.g. as in \cite{_txt2re:_????}).
\end{enumerate}

>>>>

\begin{enumerate}
\item \textbf{Syntax for pattern literals}. An ideal syntax would permit us to express patterns concisely and clearly. For example, The BisI restriction enzyme cuts DNA whenever it sees the pattern \texttt{GC\textit{N}GC}, where \texttt{\textit{N}} represents any base. We would want to express it, perhaps, as follows (using curly braces to splice one pattern into another):
\begin{lstlisting}[numbers=none]
let N : Pattern = <SURLA|T|G|CEURL>
let BisI : Pattern = <SURLGC{EURLNSURL}GCEURL>\end{lstlisting}
%The cognitive load of reading and writing patterns is low and patterns are parsed once at compile-time. 
Malformed patterns would result in intelligible {compile-time} errors.
\item A \textbf{type system} that ensures that key invariants related to regular expressions are statically maintained:
	\begin{enumerate}
	\item only other patterns and properly escaped strings are spliced into a pattern, to avoid splicing errors and injection attacks \cite{owasp2013, Bravenboer:2007:PIA:1289971.1289975}
	\item out-of-bounds backreferences to a captured group are not used \cite{spishak2012type}
	\item string processing operations do not lead to a string that is malformed, when well-formedness can be captured as membership in a regular language \cite{fulton-thesis,HosoyaVouillonPierce2000ICFP}
	\end{enumerate}
%When an error is found, an intelligible error message is provided.
%\item An \textbf{implementation} that partially or fully compiles known regular expressions into the efficient internal representation that will be used by the regular expression matching engine (e.g., a finite automata \cite{Thompson:1968:PTR:363347.363387}) ahead of time. In most languages, this compilation step occurs at run-time, even if the pattern is fully known at compile-time, thereby introducing performance overhead into programs. If the developer is not careful to cache compiled representations, regular expressions used repeatedly in a program might be needlessly re-compiled on each use. %By performing this step ahead-of-time, these dangers can be avoided.
\item \textbf{Editor services} to support syntax highlighting of patterns and to allow clients to refer to documentation and interactively test patterns against examples strings (e.g. \cite{IntelliJRegexp}) or even extract patterns from examples interactively (e.g. as in \cite{_txt2re:_????}).
\end{enumerate}
